### 2016-06-30 sec6_experiment.tex
Reformatting
Several reformats

\begin{table} [h]
\center
\small
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Attributes}& \textbf{Shopping} &  \textbf{GeoLife} &  \textbf{SingTaxi} \\ 
\hline 
\# objects  & 13,183 & 18,670 & 15,054\\ 
\hline
%\# average ts & 3,114  & 2,924 & 19,667 \\ 
%\hline
\# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
\hline
\# snapshots  & 16,931 & 10,699 & 44,364\\ 
\hline
\# clusters  & 211,403  & 206,704& 536,804\\
\hline
avg. cluster size  & 171 & 223 & 484\\
\hline
\end{tabular}
\caption{Statistics of data set}
\label{exp:dataset}
\end{table}

\textbf{Parameters}: To systematically study the performance of
our algorithms, we conduct experiments on various parameter settings. The parameters to be evaluated are listed in Table~\ref{tbl:parameters}, with default settings in bold. 
\begin{table}[h]
\small
\begin{tabular}{c|l|l}
\hline 
\textbf{Variables} & \textbf{Meaning} & \textbf{Values} \\ 
\hline 
M & min size of object set &  5, 10,  \textbf{15}, 20, 25 \\ 
\hline 
K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
\hline 
L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
\hline 
G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
\hline
$O_r$ & ratio of objects & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
$T_r$ & ratio of snapshots & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
N & number of machines & 1, 3, 5, 7, 9, \textbf{11}\\ 
\hline 
\end{tabular} 
\caption{Variables and their default values}
\label{tbl:parameters}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|}
\hline 
\textbf{Data Set} & \textbf{Shopping} & \textbf{GeoLife} & \textbf{Taxi} \\ 
\hline 
Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
\hline 
After pruning & 76,672 & 123,410 & 270,921 \\ 
\hline 
Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
\hline 
\end{tabular}

\caption{Pruning power of SPARE}
\label{tbl:pruning}
\end{table}

\begin{figure}[h]
\centering
	  \includegraphics[width=0.3\textwidth]{/exp/spare/detail.eps}
    \caption{Breakdown of cost of SPARE and SPARE-RD}
    \label{exp:wl}
%	\begin{subfigure}[b]{0.3\textwidth}
%        \includegraphics[width=\textwidth]{/exp/spare/detail.eps}
%        \caption{Decomposed running time}
%    \end{subfigure}
%    
% 	\begin{subfigure}[b]{0.22\textwidth}
%       \includegraphics[width=\textwidth]{/exp/spare/wl-shopping.eps}
%       \caption{Workload in Shopping}
%   \end{subfigure}
%    \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/spare/wl-geolife.eps}
%        \caption{Workload in Geolife}
%    \end{subfigure}  
%    \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/spare/wl-taxi.eps}
%        \caption{Workload in Taxi}
%    \end{subfigure}
%\caption{Load balance of SPARE and SPARE-LB}
\end{figure}

\begin{table}[h]
\centering \small
\begin{tabular}{|l|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{l|}{\textbf{SPARE-RD}} & \multicolumn{2}{l|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
  \caption{Statistics of execution time among executors (in seconds)}
  \label{tbl:strags}
\end{table}

@@

\subsection{Scalability}
Finally, we examine the scalability of our proposed frameworks in two contexts. First, we use single-node mode and examine the performance with multi-cores. We also compare it with the  state-of-the-art solutions for swarm and platoon patterns since they were designed  to run in a centralized server. Second, we examine the pattern detection time with increasing computing resources (number of machines). The results are reported in Figure~\ref{exp:scalability}. First, the centralized schemes are not suitable to discover patterns in large-scale trajectory databases. It takes nearly $16$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. In contrast, when utilizing the multi-core environment, our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. Second, we see that both TRPM and SPARE demonstrate promising scalability in terms of the number of machines available. The running time almost decreases linearly as more machines are used. When there are $11$ nodes in the cluster, the performance of SPARE is $94$ times better than the state-of-the-art \emph{platoon} detector in a centralized server.

\begin{figure*}[t]
\centering
\begin{subfigure}[b]{0.31\textwidth}
    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
        \caption{Shopping vary $N$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
        \caption{Geolife vary $N$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
        \caption{Taxi vary $N$}
    \end{subfigure}
 \caption{Comparisons among TRMP, SPARE and Platoon}
 \label{exp:scalability}
\end{figure*}

>>>>

\begin{table} [h]
\center
\small
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Attributes}& \textbf{Shopping} &  \textbf{GeoLife} &  \textbf{SingTaxi} \\ 
\hline 
\# objects  & 13,183 & 18,670 & 15,054\\ 
\hline
%\# average ts & 3,114  & 2,924 & 19,667 \\ 
%\hline
\# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
\hline
\# snapshots  & 16,931 & 10,699 & 44,364\\ 
\hline
\# clusters  & 211,403  & 206,704& 536,804\\
\hline
avg. cluster size  & 171 & 223 & 484\\
\hline
\end{tabular}
\caption{Statistics of datasets.}
\label{exp:dataset}
\end{table}

\textbf{Parameters}: To systematically study the performance of
our algorithms, we conduct experiments on various parameter settings. The parameters to be evaluated are listed in Table~\ref{tbl:parameters}, with default settings in bold. 
\begin{table}[h]
\small
\begin{tabular}{c|l|l}
\hline 
\textbf{Variables} & \textbf{Meaning} & \textbf{Values} \\ 
\hline 
M & min size of object set &  5, 10,  \textbf{15}, 20, 25 \\ 
\hline 
K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
\hline 
L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
\hline 
G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
\hline
$O_r$ & ratio of objects & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
$T_r$ & ratio of snapshots & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
N & number of machines & 1, 3, 5, 7, 9, \textbf{11}\\ 
\hline 
\end{tabular} 
\caption{Variables and their default values.}
\label{tbl:parameters}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|}
\hline 
\textbf{Dataset} & \textbf{Shopping} & \textbf{GeoLife} & \textbf{Taxi} \\ 
\hline 
Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
\hline 
After pruning & 76,672 & 123,410 & 270,921 \\ 
\hline 
Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
\hline 
\end{tabular}

\caption{Pruning power of SPARE.}
\label{tbl:pruning}
\end{table}

\begin{figure}[h]
\centering
	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail.eps}
    \caption{Breakdown of cost of SPARE and SPARE-RD}
    \label{exp:wl}
\end{figure}

\begin{table}[h]
\centering \small
\begin{tabular}{|l|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{l|}{\textbf{SPARE-RD}} & \multicolumn{2}{l|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
  \caption{Statistics of execution time among executors (in seconds).}
  \label{tbl:strags}
\end{table}

@@

\subsection{Scalability}
Finally, we examine the scalability of our proposed frameworks in two contexts. 
First, we use the single-node mode and examine the performance with multi-cores. 
We also compare it with the state-of-the-art solutions for swarm and platoon patterns 
since they were designed to run in a centralized server. 
Second, we examine the pattern detection time with increasing computing resources (number of machines). 
To support swarm and platoon, we sample 60\% of each dataset for this experiments. 
The results are reported in Figure~\ref{exp:scalability}. 
First, the centralized schemes are not suitable to discover patterns in 
large-scale trajectory databases. It takes nearly $30$ hours to 
detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
In contrast, when utilizing the multi-core environment, 
SPARE achieves $8$ times speed up compared to \emph{platoon} and $22$ times speed up compared to \emph{swarm}. 
%our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
Second, we see that both TRPM and SPARE demonstrate promising scalability in terms of the number of machines available. The running time almost decreases inversely as more machines are used. 
When there are $11$ nodes in the cluster, 
the performance of SPARE is $73$ times faster 
than \emph{platoon} and $170$ times better than \emph{swarm}.
%state-of-the-art \emph{platoon} detector in a centralized server.

\begin{figure*}[t]
\centering
\begin{subfigure}[b]{0.31\textwidth}
    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
        \caption{Shopping vary $N$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
        \caption{Geolife vary $N$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
        \caption{Taxi vary $N$}
    \end{subfigure}
 \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM}
 \label{exp:scalability}
\end{figure*}
